Migration Experience Trajectories: Subtitle TBD

### 2022-05-12 preregistration/Preregistration3MPCA.Rmd

@@

**Registration prior to accessing the data**. As of the date of submission, the data exist, but have not been accessed by you or your collaborators. Commonly, this includes data that has been collected by another researcher or institution.

>>>>

Recent calls for:   
- ABCD model (esp., affect and desire)   
- longitudinal data (for both acculturation and intergroup literature)   
- real-life data (for both acculturation and intergroup literature)

Recent developments:  
In the past, such data collections were often unfeasible because they were either physically impractical or too expensive. However, recent technological developments allow us to easily collect experience sampling data on mobile devices \citep[e.g.,][]{Keil2020} or using web-based applications \citep[e.g.,][]{Arslan2020}  
- data collection possible (e.g., ContactLogger [@Keil2020], FormR [@Arslan2020])  
- analyses become more accessible [@ODonnell2021]

Problem: HOWEVER, ...   
- unclear how do deal with this more complex data (many variables, persons, and time points)   
    - many different variables could be important    
    - how to consider them jointly (e.g., VAR, DSEM, ARIMA, cross-lagged panel analysis for testing model predictions, limited to specified lag and mean stationarity; Trajectory focused: mixed effects model, spline regressions, latent growth curve modeling, limited: often univariate outcome)   
- heterogeneity between people, over time, and across variables   
- **unclear how to identify core/important developments.** Especially across multiple variables at he same time (i.e., multiple aspects).  
- unclear which variables, time scales, and methods are useful in practice

Solution:   
- 3MPCA uses the data cube

not merely important for hypothesis generation, but also for identifying and understanding adaptive and maladaptive patterns. Allows us to identify clusters of similar individuals and developments, and whether these clusters differ in key adaptation markers (including, well-being, intergroup anxiety, outgroup trust, or societal participation).

We recently proposed that migration experiences and the resulting psychological changes (i.e., acculturation) can be structured in terms of affect, behavior, cognition, and desire developments (ABCD of acculturation). However, while there have been several calls for intensive longitudinal and real-life data on acculturation, little data has thus far investigated the development of migration experiences and no research has assessed the co-development of all four experience aspects. Yet, understanding how people differ in their migration trajectories, can be crucial in understanding adaptive and maladaptive patterns. Simultaneously clustering the person-, experience aspect-, and time level of migration experiences, using a three mode PCA, may allow to identify clusters of similar developments and whether these clusters differ in key adaptation markers (including, well-being, anxiety, trust, or societal inclusion).

@@

<!-- **Registration prior to analysis of the data**. As of the date of submission, the data exist and you have accessed it, though no analysis has been conducted related to the research plan (including calculation of summary statistics). A common situation for this scenario when a large dataset exists that is used for many different studies over time, or when a data set is randomly split into a sample for exploratory analyses, and the other section of data is reserved for later confirmatory data analysis. -->

**Registration following analysis of the data**: As of the date of submission, you have accessed and analyzed some of the data relevant to the research plan. This includes preliminary analysis of variables, calculation of descriptive statistics, and observation of data distributions. Please see cos.io/prereg for more information.
